Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-01 Draft/draft.tex
Honghao: updated section 2

@@

% Comments
\def\carl#1{{\color{blue} #1 -Carl}}
\newcommand{\hf}[1]{\textcolor{red}{#1}}

@@

\title{Robust self-testing of large entanglement with constant-sized correlations}

@@

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
has shown that the maximally entangled state with arbitrary local dimension 
can be self-tested with constant question alphabet but answer alphabet growing with
the local dimension. 
Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
of the generalized Magic Square game and Magic Pentagram game, one can robustly self-test
$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
Both the Magic Square game and the Magic Pentagram game have constant question alphabet
but answer alphabet of size $d$.

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
We denote a Hilbert space by $\calH$.  \carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
the maximally entangled state is denoted by 
\begin{align}
	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

@@

We use some basic number theory in our work. 
\begin{definition}
A primitive root of a prime number
$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$.  \carl{I'm skeptical about whether that's the standard definition.  (For example, the definition on wikipedia doesn't include that ``smallest integer'' part.)}
\end{definition}
In other words,
$r$ is the generator of $\Zd$.

%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
%\begin{align}
%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
%\end{align}
%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
%definitions and notation for now.}
%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
%unless otherwise specified, for example, the $k/r$ above.
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. 
Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0,1\}$ which corresponds to losing and winning. 
Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy beforehand.

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\carl{Check the use of notation above (``$A$'', ``$B$'').}
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;  \carl{``finite-dimensional''?}
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;  \carl{You're using ``$A$,$B$'' here still.}
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables.  \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
the finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.  \carl{The phrase ``the finite-dimensional
representation'' is confusing -- it sound like you are implying that there is only one representation.}
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a perfect strategy for 
the linear system game ($H\ux = \uc$) has \carl{Replace ``has'' with ``is given by''.}
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. \carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.  \carl{These last two sentences seem out of place -- consider rephrasing and relocating.}

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
\carl{What is the input distribution?}
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of the observables. 
The weighted CHSH inequality is true 
if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, if they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\carl{You need to cite the results that you're summarizing here (or refer to an appendix).}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.

@@

	Let $\ket{v}$ and $\ket{v'}$ be vectors with length less than equal to $1$ satisfying the relation that $\ket{v} \appd{\epsilon} \ket{v'}$

@@

@@

	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with length less than equal to $1$

@@

	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$

@@

	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with length less or equal to $1$,
	which satisfy the condition that 
		H\ket{u} \appd{\ep_1} a \ket{u}, \\

@@

	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$ and
	$\norm{\ket{v}} \appd{\ep_2} 1$ , if $\braket{u}{v} \geq 1 - \ep_3$,

@@

	Let $\ket{u}$ be a vector with length less than or equal to $1$ such that for a unitary $U$,

@@

	For $n=1$, the statement is satisfied.
	Assume it holds for $n = k-1$ and consider $n = k$, then we have
		&\norm{U^k \ket{u} - a^k\ket{u}} \\
		\leq &\norm{U} \norm{U^{k-1} \ket{\psi} - a^{k-1}\ket{\psi}} + \norm{a^{k-1}}

@@

		\leq &(k-1)\ep + \ep = k \ep,

@@

%=======================================
\section{The linear constraint test}
\label{sec:lct}
%=======================================
In this section, we introduce a linear constraint test that is satisfied by our correlation.
The linear constraint test is designed to enforce relations that should be satisfied by 
Alice and Bob's observables and it is inspired by 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the equations of the linear system game. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group}
\begin{align}
	G = \langle u, o : uou^{-1} = o^r \rangle, 
\end{align}
for some $r \in \N$ into a linear constraint test.

>>>>

\newcommand{\fC}{\mathfrak{C}}

@@

% Comments
\def\carl#1{{\color{blue} #1 -Carl}}
\newcommand{\hf}[1]{\textcolor{red}{#1}}
\newcommand{\hfc}[1]{\textcolor{red}{#1 -H.F.}}

@@

\title{Constant-sized correlations are sufficient for 
robust self-testing of maximally entangled states with unbounded dimension}

@@

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Proving robustness is harder.

@@

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
Usually, we denote a \hf{general} Hilbert space by $\calH$.  
\carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
\hfc{How about now?}
Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
the maximally entangled state is denoted by 
\begin{align}
	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

@@

We use some basic number theory in our work. 
\begin{definition}
A primitive root of a prime number
$d$ is \hf{an integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$.  \carl{I'm skeptical about whether that's the standard definition.  (For example, the definition on wikipedia doesn't include that ``smallest integer'' part.)}
\hfc{How about now?}
\end{definition}
In other words,
$r$ is the generator of $\Zd$.
\hf{In our work, we always pick $r$ to be the smallest primitive root of $d$.}

%We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
%\begin{align}
%	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
%\end{align}
%where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
%and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
%definitions and notation for now.}
%Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
%unless otherwise specified, for example, the $k/r$ above.
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \{0,1\}$, which is the scoring function. 
The score $0$ and $1$ correspond to losing and winning. 
Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy beforehand.

\hf{In our work, we consider a special case of nonlocal games, which we call a nonlocal test.
There are three differences between a nonlocal game and a nonlocal test:
\begin{itemize}
	\item only a subset of all the question pairs are given to Alice and Bob;
	\item the answer sets for different questions are different;
	\item the scoring function maps input-output pairs to real numbers $(\R)$.
\end{itemize}
}

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\hf{For simplicity we omit the tensor product between operators acting on different Hilbert spaces in the rest of the work.}

\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
In the rest of the paper, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite-dimensional Hilbert spaces $\calH_A$ and $\calH_B$; 
	\item a collection of binary observables $N_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $N_j^2 = \1$ for every $1 \leq j \leq n$; 
	\item a collection of binary observables $M_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $M_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j M_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $M_{il}M_{ik} = M_{ik}M_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables. 
\hf{More specifically, the fact that all the observables $\{M_{ij}\}_{j: H(i,j) = 1}$ commute with each other
implies that they share a common eigenspace. The collection of eigenvalues associated with one eigenstate is the assignment
to the whole equation when this eigenstate is measured in a projective measurement strategy.}
 \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
\hf{a} finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.  
\hf{Here we skip the background about group representations and presentations.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}. }
\carl{The phrase ``the finite-dimensional
representation'' is confusing -- it sound like you are implying that there is only one representation.}
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
\hf{In later parts of this work, we give the solution group instead of the set of linear equations when we defines
a linear system game.}

Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the carrier space $\C^d$, then a perfect strategy for 
the linear system game ($H\ux = \uc$) is given by 
\begin{enumerate}
	\item $M_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $N_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
	\hf{I don't think we need to take transpose because these are binary observables. -HF}
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
\hf{Later we will use this approach to construct a strategy for a linear system game.}
\carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}
\hfc{How about now?}
However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
\hf{The weighted CHSH inequality a variation of the CHSH inequality \cite{chsh}. 
We formulate it as a nonlocal test.}
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test, for $|\alpha|\geq 1$,  is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
The input distribution is $\pi(x,y) = 1/4$ for all $(x,y) \in \calX \times \calY$.
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of the observables. 
The weighted CHSH inequality is true 
if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, if they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
$ \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}$ \cite{acin2012}.
\carl{You need to cite the results that you're summarizing here (or refer to an appendix).}
\hfc{I cited the paper in the title of this subsection. Maybe I add a sentence saying that this subsection
summarizes results in \cite{acin2012}?}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$ \cite{acin2012}]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.
\hf{In \cref{sec:full_test} we design
a nonlocal test call the extended weighted CHSH test based on the weighted CHSH inequality.}

@@

	Let $\ket{v}$ and $\ket{v'}$ be vectors such that the relation $\ket{v} \appd{\epsilon} \ket{v'}$ holds,

@@

\hfc{You are right. We don't.}

@@

	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with norm less than equal to $1$

@@

	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$,

@@

	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with norm less or equal to $1$
		H\ket{u} \appd{\ep_1} a \ket{u} &&

@@

	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$,
	$\norm{\ket{v}} \appd{\ep_2} 1$, and $\braket{u}{v} \geq 1 - \ep_3$,

@@

	Let $\ket{u}$ be a vector with norm less than or equal to $1$ such that for a unitary $U$,

@@

	For $k=1$, the statement is satisfied.
	Assume it holds for $k = n-1$ and consider $k = n$, then we have
		&\norm{U^n \ket{u} - a^n\ket{u}} \\
		\leq &\norm{U} \norm{U^{n-1} \ket{\psi} - a^{n-1}\ket{\psi}} + \norm{a^{n-1}}

@@

		\leq &(n-1)\ep + \ep = n \ep,

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
In this section, we introduce a linear constraint test that is satisfied by our correlation.
The linear constraint test is designed to enforce relations that should be satisfied by 
Alice and Bob's observables and it is inspired by 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the equations of the linear system game. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group}
\begin{align}
	G = \langle u, o : uou^{-1} = o^r \rangle, 
\end{align}
for some $r \in \N$ into a linear constraint test.
